### 2017-07-18 AFS/u13.tex
progress

\documentclass[10pt, a4paper]{article}
\usepackage{amssymb}
\usepackage[utf8]{inputenc}
\usepackage[]{csquotes}
\usepackage[german]{babel}
\usepackage{graphicx}
\usepackage{amsmath,wasysym}

\begin{document}

\section*{13.Übung}
\paragraph{Sven Fiergolla 1252732}
\subsection*{Aufgabe a)}

\subsection*{Aufgabe b)}
Vorgehensweise der Maschine $U$:\\
\bigskip
Eingabe:\\
\begin{small}
\raisebox{\depth}{\rotatebox{180}{ee}};$\Square D\Square A\Square D\Square D\Square C\Square R\Square D\Square A\Square A\Square ;\Square \Square D\Square A\Square A\Square D\Square D\Square C\Square C\Square R\Square D\Square A\Square ::\Square $\\
\end{small}

Beginn in Zustand $q_0$ $\rightarrow$ $anf$\\
\begin{small}
\raisebox{\depth}{\rotatebox{180}{ee}};$\Square D\Square A\Square D\Square D\Square C\Square R\Square D\Square A\Square A\Square ;\Square \Square D\Square A\Square A\Square D\Square D\Square C\Square C\Square R\Square D\Square A\Square ::\Square : \Square D \Square A$\\
\end{small}

Zustand $anf$ $\rightarrow$ $anf$\\

\end{document}